\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[english,activeacute]{babel}

\title{Formula One General Information}
\author{Owen Millspaugh, Sreya Kalyan, Tara Prasad, Cynthia Kitners}

\begin{document}

\maketitle

\section{About the Sport}
\textbf With its inauguration in 1950, Formula 1 is the world's most prestigious motorsport championship. 
The season runs from March to December and contains 20 drivers, 10 teams, and 10 chassis.
Drivers race all over the world in races known as Grand Prixs.
The current engine manufacturers are Ferrari, Honda RBPT, Mercedes, and Renault. 
The tyre supplier is Pirelli.
\section{Data}
\subsection{Constructor Championships}
\textbf 2019: Mercedes\\
2020: Mercedes\\
2021: Mercedes\\
2022: Red Bull\\
2023: Red Bull
\subsection{Driver Championship}
2019: Lewis Hamilton\\
2020: Lewis Hamilton\\
2021: Max Verstappen\\
2022: Max Verstappen\\
2023: Max Verstappen
\subsection{Drivers}
1. Max Verstappen\\
2. Lando Norris\\
3. Charles Leclerc\\
4. Carlos Sainz\\
5. Sergio Perez\\
6. Oscar Piastri\\
7. Geroge Russell\\
8. Lewis Hamilton\\
9. Fernando Alonso\\
10. Yuki Tsunoda\\
11. Lance Stroll\\
12. Nico Hulkenburg
13. Daniel Ricciardo\\
14. Pierre Gasly\\
15. Kevin Magnussen\\
16. Esteban Ocon\\
17. Alexander Albon\\
18. Zhou Guanyu\\
19. Valteri Bottas\\
20. Logan Sareant
\subsection{Constructors}
1. Oracle Red Bull Racing\\
2. Scuderia Ferrari\\
3. McLaren Formula 1 Team\\
4. Mercedes-AMG PETRONAS F1 Team\\
5. Aston Martin Aramco F1 Team\\
6. Visa Cashapp RB Formula One Team\\
7. MoneyGram Haas F1 Team\\
8. BWT Alpine F1 Team\\
9. Williams Racing\\
10. Stake F1 Team Kick Sauber
\subsection{Main Circuits}
1. Bahrain International Circuit - Sakhir, Bahrain\\
2. Jeddah Corniche Circuit, Jeddah - Saudi Arabia\\
3. Melbourne Grand Prix Circuit - Melbourne, Australia\\
4. Suzuka International Racing Course - Suzuka, Japan\\
5. Shanghai International Circuit - Shanghai, China\\
6. Miami International Autodrome - Miami, USA\\
7. Autodromo Enzo e Dino Ferrari - Imola, Italy\\
8. Circuit de Monaco - Monte Carlo, Monaco\\
9. Circuit Gilles-Villeneuve - Montréal, Canada\\
10. Circuit de Barcelona-Catalunya - Barcelona, Spain\\
11. Red Bull Ring - Spielberg, Austria\\
12. Silverstone Circuit - Silverstone, Great Britain\\
13. Hungaroring - Budapest, Hungary\\
14. Circuit de Spa-Francorchamps - Spa-Francorchamps, Belgium\\
15. Circuit Zandvoort - Zandvoort, Netherlands\\
16. Autodromo Nazionale Monza - Monza, Italy\\
17. Baku City Circuit - Baku, Azerbaijan\\
18. Marina Bay Street Circuit - Marina Bay, Singapore\\
19. Circuit of The Americas - Austin, USA\\
20. Autódromo Hermanos Rodríguez - Mexico City, Mexico\\
21. Autódromo José Carlos Pace - São Paulo, Brazil\\
22. Las Vegas Strip Circuit - Las Vegas, USA\\
23. Lusail International Circuit - Doha, Qatar\\
24. Yas Marina Circuit - Yas Island, Abu Dhabi


\end{document}
